Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-02 paper.tex
Fix some merge issues and add more results. Plus some tidy ups.

\usepackage{cvpr2019AuthorKit/latex/cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
% \usepackage{arydshln}
\usepackage{subcaption}

@@

\noindent {\bf Vehicle Re-Identification. }
Whist vehicle re-id is less studied than person re-id
\cite{gong2014person,li2014deepreid,ahmed2015improved,xiao2016learning,li2017person,sun2017svdnet,li2018harmonious,zhong2017camera},
there are a handful of existing methods.
%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based re-id method. 
%The vehicles are firstly classified by different attributes like car model types and colours. The re-id matching is then conducted in the attribute space.
%%
%Dominik \etal \cite{zapletal2016vehicle}
%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs. 
%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
%%
%Both methods rely heavily on weak hand-crafted visual features in a
%complex multi-step based approach, suffering from weak discriminative model generalisation.

@@

\section{Multi-modal Vehicle Re-identification}
\begin{figure*}
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tabular}{c | c | c}
      \hline
      Index & Orientation & Colour \\
      \hline
      0 & front & \textcolor{red}{red} \\
      1 & rear & \textcolor{blue}{blue}  \\
      2 & left  & - \\
      3 & left front & \textcolor{cyan}{cyan}  \\
      4 & left rear & \textcolor{yellow}{yellow}  \\
      5 & right  & - \\
      6 & right front & \textcolor{green}{green} \\
      7 & right rear & \textcolor{black}{black} \\
      \hline
    \end{tabular}
  \end{subfigure}
  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
  \label{T:veri_veh_orientations}
\end{figure*}

@@

\paragraph{(B) Multi-scale Analysis}

@@

The loss for this branch is then calculated across the minibatch of images as:
\begin{equation}
  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}\log{p_i^{ID}} + \frac{1}{N_S} \sum_{i=1}^{N_B}q_i^O
\end{equation}
where $N_S$ is the size of the subset of the minibatch for which orientation labels are known, and
\[
q_i^O =
\begin{cases}
    \log{p_i^{O}} & \text{if } o_i \in \mathcal{O} \\
    0 & \text{otherwise}
\end{cases}
\]
%% \paragraph{(E) Vehicle Landmark Localisation}

@@

We employ the ResNet50 \cite{} network architecture as the base of our model.

Details:
- Learning rate of 0.0001
- Batch size 8
- Number of epochs.
- Adam optimiser with exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$.
- The two scales used: standard $224\x224$ and small (for multiscale) $160\x160$.

@@

Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset. As can be seen, our model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of ... and ... respectively.

After 100 epochs

\begin{table}
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    \hline
    MTML-S & 59.4 & 89.7 & 95.1 \\
    MTML-O & \\
    MTML-G & \\
    % \hdashline
    MTML-SG & 63.4 & 91.1 & 95.4 \\
    MTML-OG & \\
    MTML-OSG & \bf{61.8} & \bf{90.3} & \bf{95.4} \\
    \hline
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
    MTML-OSG (ReRank) & \bf{65.8} & \bf{91.9} & 94.0 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}

>>>>

\usepackage{cvpr2019AuthorKit/latex/cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{subcaption}

@@

\noindent {\bf Vehicle Re-Identification. }
Whist vehicle re-id is less studied than person re-id
\cite{gong2014person,li2014deepreid,ahmed2015improved,xiao2016learning,li2017person,sun2017svdnet,Li2018Harmonious,zhong2017camera},
there are a handful of existing methods.
%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based re-id method.
%The vehicles are firstly classified by different attributes like car model types and colours. The re-id matching is then conducted in the attribute space.
%%
%Dominik \etal \cite{zapletal2016vehicle}
%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs.
%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
%%
%Both methods rely heavily on weak hand-crafted visual features in a
%complex multi-step based approach, suffering from weak discriminative model generalisation.

@@

\section{Multi-modal Vehicle Re-identification}
\begin{figure*}
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tabular}{c | c | c}
      \hline
      Index & Orientation & Colour \\
      \hline
      0 & front & \textcolor{red}{red} \\
      1 & rear & -  \\
      2 & left  & - \\
      3 & left front & \textcolor{cyan}{cyan}  \\
      4 & left rear & \textcolor{yellow}{yellow}  \\
      5 & right  & - \\
      6 & right front & \textcolor{green}{green} \\
      7 & right rear & \textcolor{black}{black} \\
      \hline
    \end{tabular}
  \end{subfigure}
  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
  \label{T:veri_veh_orientations}
\end{figure*}

@@

\paragraph{(B) Identity from Scaled Image}

@@

The loss for this branch is then calculated across the minibatch of images as:
\begin{equation}
  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}\log{p_i^{ID}} + \frac{1}{N_S} \sum_{i=1}^{N_B}q_i^O
\end{equation}
where $N_S$ is the size of the subset of the minibatch for which orientation labels are known, and
\[
q_i^O =
\begin{cases}
    \log{p_i^{O}} & \text{if } o_i \in \mathcal{O} \\
    0 & \text{otherwise}
\end{cases}
\]

%% \paragraph{(E) Vehicle Landmark Localisation}

@@

We employ the ResNet50 \cite{} network architecture as the base of our model. We train the model with minibatches of size 8, using the Adam optimisation technique with a learning rate of 0.0001, exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$. The two image sizes used were standard $224\x224$ and small (for the scaled branch) $160\x160$.

@@

Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset. All experiments we continued for 150 epochs of training. As can be seen, even before re-ranking, our full model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of 64.6 and 92.3 respectively. And after re-ranking the mAP score is increased to an impressive 68.3.

\emph{TODO more detailed discussion of results}

\begin{table}
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
    \hline
    MTML-S & 59.4 & 89.5 & 94.9 \\
    MTML-O & 60.8 & 90.2 & 95.4 \\
    MTML-G \emph{TODO} & 62.8 & 90.9 & 96.2 \\
    \hdashline
    MTML-SG & 63.7 & 90.6 & 95.8 \\
    MTML-OG & 63.5 & 92.0 & \bf{96.4}\\
    MTML-OSG & \bf{64.6} & \bf{92.3} & 95.7 \\
    \hdashline
    MTML-OSG (ReRank) & \bf{\emph{68.3}} & 92.0 & 94.2 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}
